Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-16 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item Background and Literature Review
    	\item Proposed Research
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community of web services
        \item Goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Facilitate Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item {\bf Background and Literature Review}
    	\item Proposed Research
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Communities of Web Services}
    \begin{frame}{Community of Web Services}
        Communities of Web Services
        \begin{itemize}
            \item Ease and improve the process of Web services discovery in an open environment like the Internet
        	\item Improve service quality, availability and responsiveness
        \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
    	\item Time Line
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame30 outline page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Milestones}
\begin{frame}{Milestones}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
    	\item {\bf Time Line}
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Line}
    \begin{frame}{Time Line}

@@

    \begin{enumerate}
        \item Published a paper in 10th International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"} {\color{blue} (Accepted)}
        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing {\color{blue} (Second round of review)}
        \item Submitted a Paper to the 10th International Conference on Service Oriented Computing (ICSOC 2012); \emph{"Analyzing Coopetition Strategies of Services within Communities"} {\color{blue} (Accepted)}
        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing; \emph{"To Compete or to Cooperate? This is the Question in Communities of Autonomous Services"}
    \end{enumerate}

>>>>

\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item Background and Literature Review
    	\item Proposed Research
    	\item Timeline and Feature Work
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community of web services, Goals:        
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Facilitate Web Service Discovery over Internet}.
            \item \textbf{Maintaining high reputation and market share}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item {\bf Background and Literature Review}
    	\item Proposed Research
    	\item Timeline and Feature Work
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Communities of Web Services}
    \begin{frame}{Community of Web Services}
        Communities of Web Services
        \begin{itemize}
            \item Ease and improve the process of Web services discovery in an open environment like the Internet
        	\item Improve service quality, availability and responsiveness
            \item Maintaining high reputation and market share
        \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
    	\item Timeline and Feature Work
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame30 outline page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Milestones}
\begin{frame}{Milestones}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
    	\item {\bf Timeline and Feature Work}
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeline}
    \begin{frame}{Timeline}

@@

    \begin{enumerate}
        \item Published a paper in 10th International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"} {\color{blue} (Accepted)}
        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing {\color{blue} (Second round of review)}
        \item Submitted a Paper to the 10th International Conference on Service Oriented Computing (ICSOC 2012); \emph{"Analyzing Coopetition Strategies of Services within Communities"} {\color{blue} (Accepted)}
        \item Submitted a Journal Paper to the International Journal of Expert Systems With Applications; IEEE Transactions on Services Computing; \emph{"To Compete or to Cooperate? This is the Question in Communities of Autonomous Services"}
    \end{enumerate}
